Active Damping of Rotating Positioning Platforms

### 2020-06-24 paper/paper.tex
Add figure to show the opt gain on the root locus

% Created 2020-06-23 mar. 19:34
% Intended LaTeX compiler: pdflatex
\documentclass{ISMA_USD2020}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author[1,3] {T. Dehaeze}
\author[1,2] {C. Collette}
\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
\bibliographystyle{IEEEtran}
\usepackage{tikz}
\usetikzlibrary{shapes.misc}
\date{}
\title{Active Damping of Rotating Positioning Platforms}
\hypersetup{
 pdfauthor={},
 pdftitle={Active Damping of Rotating Positioning Platforms},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
 pdflang={English}}
\begin{document}

@@

\section{Introduction}
\label{sec:org977317c}
\label{sec:introduction}
Controller Poles are shown by black crosses (
\begin{tikzpicture} \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){}; \end{tikzpicture}
).
\cite{dehaeze18_sampl_stabil_for_tomog_exper}

\section{System Under Study}
\label{sec:org042e800}
\subsection{Rotating Positioning Platform}
\label{sec:org489e4b9}
Consider the rotating X-Y stage of Figure \ref{fig:rotating_xy_platform}.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system.pdf}
\caption{\label{fig:rotating_xy_platform}Figure caption}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\linewidth]{figs/cedrat_xy25xs.jpg}
\caption{\label{fig:cedrat_xy25xs}Figure caption}
\end{figure}

\subsection{Equation of Motion}
\label{sec:orgb1836d5}
The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\).

@@

\subsection{Transfer Functions in the Laplace domain}
\label{sec:orgb1002ed}

@@

\subsection{Constant Rotating Speed}
\label{sec:orga4faf60}
To simplify, let's consider a constant rotating speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/campbell_diagram.pdf}
\caption{\label{fig:campbell_diagram}Campbell Diagram}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_compare_rotating_speed.pdf}
\caption{\label{fig:plant_compare_rotating_speed}Caption}
\end{figure}

\section{Integral Force Feedback}
\label{sec:orgaf500b0}
\subsection{Control Schematic}
\label{sec:orgbd9f859}

@@

\subsection{Equations}
\label{sec:org48206d5}
The sensed forces are equal to:
\begin{equation}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
\begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
\begin{bmatrix} d_u \\ d_v \end{bmatrix}
\end{equation}

@@

\subsection{Plant Dynamics}
\label{sec:orgec8431d}

@@

\subsection{Physical Interpretation}
\label{sec:org159680e}

@@

\section{Integral Force Feedback with High Pass Filters}
\label{sec:org694707d}
\subsection{Modification of the Control Low}
\label{sec:org931fb10}

\subsection{Close Loop Analysis}
\label{sec:org9de0aa7}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_modified_iff_ter.pdf}
\caption{\label{fig:root_locus_modified_iff}Figure caption}
\end{figure}

\subsection{Optimal Cut-Off Frequency}
\label{sec:org9808de1}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_wi_modified_iff_bis.pdf}
\caption{\label{fig:root_locus_wi_modified_iff}Figure caption}
\end{figure}

@@

\section{Integral Force Feedback with Parallel Springs}
\label{sec:orgd4915d5}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/rotating_xy_platform_springs.pdf}
\caption{\label{fig:rotating_xy_platform_springs}Figure caption}
\end{figure}

@@

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_iff_kp_ter.pdf}
\caption{\label{fig:root_locus_iff_kp_bis}Figure caption}
\end{figure}

@@

\section{Direct Velocity Feedback}
\label{sec:orgb0a5870}

@@

\section{Comparison of the Proposed Active Damping Techniques}
\label{sec:org6097c1d}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/comp_compliance.pdf}
\caption{\label{fig:comp_compliance}Figure caption}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/comp_transmissibility.pdf}
\caption{\label{fig:comp_transmissibility}Figure caption}
\end{figure}

\section{Conclusion}
\label{sec:org1624a6b}
\label{sec:conclusion}

\section*{Acknowledgment}
\label{sec:org1b29790}

>>>>

% Created 2020-06-24 mer. 15:36
% Intended LaTeX compiler: pdflatex
\documentclass{ISMA_USD2020}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage{subcaption}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author[1,3] {T. Dehaeze}
\author[1,2] {C. Collette}
\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
\bibliographystyle{IEEEtran}
\usepackage{tikz}
\usetikzlibrary{shapes.misc}
\date{}
\title{Active Damping of Rotating Positioning Platforms}
\hypersetup{
 pdfauthor={},
 pdftitle={Active Damping of Rotating Positioning Platforms},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
 pdflang={English}}
\begin{document}

@@

\section{Introduction}
\label{sec:orgbec19fa}
\label{sec:introduction}
Controller Poles are shown by black crosses (
\begin{tikzpicture} \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){}; \end{tikzpicture}
).

\section{Dynamics of Rotating Positioning Platforms}
\label{sec:org81be86a}
\subsection{Studied Rotating Positioning Platform}
\label{sec:orgf8fad9b}
Consider the rotating X-Y stage of Figure \ref{fig:system}.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system.pdf}
\caption{\label{fig:system}Figure caption}
\end{figure}

\subsection{Equation of Motion}
\label{sec:org926ba54}
The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\).

@@

\subsection{Transfer Functions in the Laplace domain}
\label{sec:org298e237}

@@

\subsection{Constant Rotating Speed}
\label{sec:org8d2eda6}
To simplify, let's consider a constant rotating speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).

@@

\begin{figure}[htbp]
\begin{subfigure}[c]{0.4\linewidth}
\includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
\caption{\label{fig:campbell_diagram_real} Real Part}
\end{subfigure}
\begin{subfigure}[c]{0.4\linewidth}
\includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
\caption{\label{fig:campbell_diagram_imag} Imaginary Part}
\end{subfigure}
\caption{\label{fig:campbell_diagram}Campbell Diagram}
\centering
\end{figure}

@@

\begin{figure}[htbp]
\begin{subfigure}[c]{0.45\linewidth}
\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms \(d_u/F_u\), \(d_v/F_v\)}
\end{subfigure}
\begin{subfigure}[c]{0.45\linewidth}
\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\), \(d_u/F_v\)}
\end{subfigure}
\caption{\label{fig:plant_compare_rotating_speed}Dynamics}
\centering
\end{figure}

\section{Integral Force Feedback}
\label{sec:org2e8c85f}
\subsection{Control Schematic}
\label{sec:org50b6359}

@@

\subsection{Equations}
\label{sec:org99c13a7}
The sensed forces are equal to:
\begin{equation}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
\begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
\begin{bmatrix} d_u \\ d_v \end{bmatrix}
\end{equation}

@@

\subsection{Plant Dynamics}
\label{sec:org1e476e3}

\subsection{Integral Force Feedback}
\label{sec:orga5d8887}

@@

@@

\section{Integral Force Feedback with High Pass Filters}
\label{sec:org569b7db}
\subsection{Modification of the Control Low}
\label{sec:org4d0c1ca}

\subsection{Feedback Analysis}
\label{sec:org1f34d25}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
\caption{\label{fig:root_locus_modified_iff}Figure caption}
\end{figure}

\subsection{Optimal Cut-Off Frequency}
\label{sec:org04a5aa4}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_wi_modified_iff.pdf}
\caption{\label{fig:root_locus_wi_modified_iff}Figure caption}
\end{figure}

@@

\section{Integral Force Feedback with Parallel Springs}
\label{sec:org03c54a4}
\subsection{Stiffness in Parallel with the Force Sensor}
\label{sec:orgc2d9221}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system_parallel_springs.pdf}
\caption{\label{fig:system_parallel_springs}Figure caption}
\end{figure}

\subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
\label{sec:org8097ba5}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_iff_kp.pdf}
\caption{\label{fig:root_locus_iff_kp}Figure caption}
\end{figure}

\subsection{Optimal Parallel Stiffness}
\label{sec:org1f2e167}

@@

@@

\section{Direct Velocity Feedback}
\label{sec:orgda2e325}
\subsection{Control Schematic}
\label{sec:org0e84009}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system_dvf.pdf}
\caption{\label{fig:system_dvf}Figure caption}
\end{figure}

\subsection{Equations}
\label{sec:org7cc244c}

\subsection{Relative Direct Velocity Feedback}
\label{sec:org668d842}

@@

\section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
\label{sec:orgade0126}
**

**

@@

\subsection{Transmissibility and Compliance}
\label{sec:org59b0db2}

\begin{figure}[htbp]
\begin{subfigure}[c]{0.45\linewidth}
\includegraphics[width=\linewidth]{figs/comp_compliance.pdf}
\caption{\label{fig:comp_compliance} Transmissibility}
\end{subfigure}
\begin{subfigure}[c]{0.45\linewidth}
\includegraphics[width=\linewidth]{figs/comp_transmissibility.pdf}
\caption{\label{fig:comp_transmissibility} Compliance}
\end{subfigure}
\caption{\label{fig:comp_active_damping}Comparison of the three proposed Active Damping Techniques}
\centering
\end{figure}

\section{Conclusion}
\label{sec:org4b70853}
\label{sec:conclusion}

\section*{Acknowledgment}
\label{sec:org7708a14}
